---
title: "Getting Started with BulkRNAseqTool"
author: "John Doe"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

BulkRNAseqTool is an R package designed to streamline bulk RNA-seq data analysis. This vignette will guide you through the basic workflow.

## Installation

```{r install, eval = FALSE}
# Install from GitHub
remotes::install_github("yourusername/BulkRNAseqTool")

# Load the package
library(BulkRNAseqTool)
```

## Basic Workflow

### Initialize Analysis Object

```{r init}
analysis <- BulkRNASeqAnalysis$new(output_root = "my_first_analysis")
```

### Add Tasks

```{r add_tasks}
analysis$add_task(
  "process_counts",
  process_counts_matrix_task,
  params = list(
    counts_path = system.file("extdata/sample_data/raw_counts.txt", package = "BulkRNAseqTool"),
    gene_mapping_path = system.file("extdata/sample_data/gene_mapping.txt", package = "BulkRNAseqTool")
  )
)

analysis$add_task("filter_genes", filter_low_expression_task)
analysis$add_task("prepare_dge", prepare_dge_analysis_task)
analysis$add_task("dge", perform_dge_analysis_task)
analysis$add_task("volcano", generate_volcano_plots_task)
```

### Run Pipeline

```{r run_pipeline, eval = FALSE}
analysis$run_pipeline()
```

## Output Structure

After running the analysis, your results directory will have the following structure:

```
my_first_analysis/
├── 00_data/       # Processed count matrices
├── 01_check/      # QC reports and visualizations
├── 02_DEG/        # Differential expression results
├── logs/          # Analysis logs
└── results/       # Summary results
```

## Customizing Parameters

You can customize analysis parameters:

```{r custom_params}
# Modify default parameters
analysis$params$perform_dge_analysis$alpha <- 0.01
analysis$params$perform_dge_analysis$fc <- 1.5

# Run with updated parameters
analysis$run_pipeline(c("dge", "volcano"))
```

## Creating Custom Tasks

```{r custom_task}
# Define custom task function
custom_volcano_task <- function(self, output_dir = "custom_volcano", ...) {
  # Access DEG results
  deg_results <- self$results$dge
  
  # Custom volcano plot code
  # ...
  
  return(list(plot_path = "custom_volcano/plot.pdf"))
}

# Add custom task
analysis$add_task("custom_volcano", custom_volcano_task)
analysis$run_pipeline("custom_volcano")
```

## Next Steps

For more advanced usage, see:
- `vignette("Advanced-Analysis", package = "BulkRNAseqTool")`
- `?BulkRNASeqAnalysis`
- `?perform_gsea_analysis`
